\label{INFORMEDOverview}
\informed\ is the Altran method for the construction of high-quality
software at a low-cost, it uses elements of both object oriented (OOD) and functional
 design. OOD is used to establish the architecture of the system and the
 elements of system state it contains. The result is an annotated framework
 of SPARK packages, constructing an architecture that is modifiable and
 maintainable, which is capable of being analysed at an early stage using the Examiner.

Altrans' analysis of many software designs has identified that there are 3 key building
 blocks that are used repeatedly to build an application. These building blocks are:
   \begin{itemize}
  \item A Main Program, that is the top level, entry point controlling the behaviour
   a system or sub-system.
  \item Variable Packages, which are SPARK packages containing persistent "state",
   and are equivalent to what is commonly called an object.
  \item Type Packages, which define the name of a type, and the operations taht
  it supports.
  \end{itemize}

In addition to these packages, \informed\ also includes two other types of packages:
   \begin{itemize}
  \item Utility Packages, which provide shared functionality. The need for utility packages
  arises when an operation is required which affects or uses more than one variable of type
  package.
  \item Boundary Variable Packages, which are particular kinds of variable package which
  provides interfaces between the software functionality described by the \informed\ design
  and elements outside it with which it must communicate. Unlike other variable packages the
  variable within the package is a place holder representing the stream of data arriving from,
  or being sent to, the outside world rather than simply an abstract name for the internal state
  of the package.
  \end{itemize}

The \informed\ method consists of 6 steps, and these are:
   \begin{enumerate}
  \item Identification of the System boundary, inputs and outputs.
  \item Identification of the SPARK boundary.
  \item Identification and localization of the system state.
  \item Handling initalization of state.
  \item Handling secondary requirements.
  \item Implementing the internal behaviour of components.
  \end{enumerate}

The output of the \informed\ process is represented a collection of design diagrams and a collection
of well defined SPARK specifications. A summary of the \informed\ graphical elements and example
representations are documented in Annex A of this document to aid the reader in the understanding of 
the architectural design.

As the VSTTE 2013 competition has a very short timescale, it is not expected that there is enough
time to fully apply the \informed\ process, however the benefits of the benifits of the modelling
approach and the translation in SPARK Package Specifications can be shown in this project.
