\paragraph{Alan Newton}
is a senior software engineer working for Altran in Bath. He has a PhD
in Software Engineering, and has experience throughout the
lifecycle. Not only has he experience in developing high-integrity
software using Formal Methods and \spark, he has also developed novel
tools and processes for the effective deployment of software
engineering activities.

In this project Alan has been involved in developing the processes,
applying the \reveal\ and \informed\ processes and developing
documentation to support the delivery of the project.

\paragraph{Florian Schanda}
is a member of the \spark\ team at Altran in Bath, currently
responsible for the new flow analysis engine of the \spark 2014 tools
and Riposte, the counter-example generator of \spark. Previously he
has written \spark\ code for a large Altran software project. He holds
a PhD in computer science from the University of Bath.

\shouldDo{In this project Florian...}

\paragraph{Yannick Moy}
is a senior engineer at AdaCore, working on static analysis and formal
verification tools for Ada and \spark\ programs. He previously worked
on similar tools for C/C++ programs at PolySpace, INRIA research labs,
and Microsoft Research. Moy received a PhD in formal program
verification from Universit\'e Paris-Sud.

In this project, Yannick has been involved in developing formal
specifications, implementing code, and verifying (formally and by testing)
that the code matches the formal specifications.

\paragraph{Matteo Bordin}
\shouldDo{Some text about Matteo}

\paragraph{David Mentr\' e}
is a research engineer at Mitsubishi Electric R\&D Centre Europe,
working on the application of formal methods to industrial product
development. He received a PhD in Computer Science from Rennes~1
University.

\shouldDo{In this project, David has been involved in...}
